Results

### 2024-11-29 Analysis/04_Summarise_results.Rmd
fixed p-value selection in fancy plots
bug came from added ses column

```{r, echo = FALSE}
# rownames(model_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
change.names <- function(table, fancy_names, output = "xtable", colnames = FALSE) {
  if(output == "xtable") {
    ## Format the row names for xtable
    ## split should be \\ and the third element should be \texttt{}
    row_names <- sapply(fancy_names, strsplit, split = "\\n")
    add.ttt <- function(x) {
      x[[3]] <- paste0("\\texttt{", x[[3]], "}")
      return(x)
    }
    row_names <- lapply(row_names, add.ttt)
    row_names <- lapply(row_names, function(x) paste(x, collapse = "\\\\"))
  }
  if(colnames) {
    colnames(table) <- gsub("equalizing", "EQ", colnames(table))
    colnames(table) <- gsub("facilitation", "FA", colnames(table))
    colnames(table) <- gsub("filtering", "FI", colnames(table))
    colnames(table) <- gsub("competition", "CO", colnames(table))
    colnames(table) <- gsub("rm", "", colnames(table))
  }
  rownames(table) <- row_names
  return(table)
}
# kable(model_table_2d, caption = "Results of the model scaled metric ~ removal level per stressor (2D)", align = "c")
print(xtable(change.names(model_table_2d, fancy_names), caption = "Results of the model scaled metric ~ removal level per stressor (2D)"), file = "../Manuscript/Tables/results_model2d.tex")

@@

```{r, echo = FALSE}
print(xtable(change.names(null_table_2d[, 1:8], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences2d_1.tex")

>>>>

```{r, echo = FALSE, eval = FALSE}
# rownames(model_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
change.names <- function(table, fancy_names, output = "xtable", colnames = FALSE) {
  if(output == "xtable") {
    ## Format the row names for xtable
    ## split should be \\ and the third element should be \texttt{}
    row_names <- sapply(fancy_names, strsplit, split = "\\n")
    add.ttt <- function(x) {
      x[[3]] <- paste0("\\texttt{", x[[3]], "}")
      return(x)
    }
    row_names <- lapply(row_names, add.ttt)
    row_names <- lapply(row_names, function(x) paste(x, collapse = "\\\\"))
  }
  if(colnames) {
    colnames(table) <- gsub("equalizing", "EQ", colnames(table))
    colnames(table) <- gsub("facilitation", "FA", colnames(table))
    colnames(table) <- gsub("filtering", "FI", colnames(table))
    colnames(table) <- gsub("competition", "CO", colnames(table))
    colnames(table) <- gsub("rm", "", colnames(table))
  }
  rownames(table) <- row_names
  return(table)
}
# kable(model_table_2d, caption = "Results of the model scaled metric ~ removal level per stressor (2D)", align = "c")
print(xtable(change.names(model_table_2d, fancy_names), caption = "Results of the model scaled metric ~ removal level per stressor (2D)"), file = "../Manuscript/Tables/results_model2d.tex")

@@

```{r, echo = FALSE, eval = FALSE}
print(xtable(change.names(null_table_2d[, 1:8], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences2d_1.tex")
